Objectification in Action: Self- and Other-Objectification in Same-gender Interactions

### 2020-11-10 Final_Manuscript.Rmd
tabled measures

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---
```{r setup, analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, include = FALSE)
```
```{r packages, warning = FALSE, message = FALSE}
library(papaja)
library(nlme)
library(haven)
library(devtools)
library(psych)
library(mosaic)
#library(dyadr)
library(tidyr)
library(dplyr)
library(irr)
library(apaTables)
library(knitr)
library(kutils)
library(tidyverse)
library(lavaan)
library(xtable)
library(rmarkdown)
```
@robertsfredrickson's Objectification Theory, suggests that, in addition to being steeped in a culture that objectifies women, women are objectified in actual interpersonal encounters. The negative effects of this interpersonal objectification for women have been theorized to be the strongest under the "male gaze," that is, when it is a perceived or actual man doing the objectifying [@calogero2004test; @gervais2011you; @gay2010my], but what are the consequences when a woman objectifies another woman in an interaction? Psychological researchers studying the sexual objectification of women have in recent years explored the interpersonal process of the objectification, finding evidence for *self*-objectification in the target as a proximal consequence of being objectified [@garcia2016objectification; @strelan2018birds; @riemer2020self]. In a recent review, @gervais2020social organized the extant literature on interpersonal self-objectification and proposed a theoretical model called the Social Interaction Model of Objectification (SIMO). The SIMO focuses on understanding mixed-gender interactions, acknowledging the patriarchal power structure embedded in these mixed interactions, but can it be extended to interactions among women? Although there is evidence that women can objectify other women [@loughnan2015exploring; @puvia2013being; @gervais2013my], studies investigating the process of interpersonal objectification in interactions between women is scarce.

@@

```{r measures, include=TRUE, echo=FALSE, results='asis'}
#Cognitive performance - Full sample
mean_trigram <- favstats(~trigram_score_A, data=clarksmith_women)$mean
sd_trigram <- favstats(~trigram_score_A, data=clarksmith_women)$sd

##SOO
#Clark
clark_extsoo_alpha <- psych::alpha(select(clark_final, otherint_1, otherint_2, 
                                          otherint_5, otherint_6, otherint_10))$total[2]
clark_intsoo_alpha <- psych::alpha(select(clark_final, otherint_3, otherint_4, 
                                          otherint_7, otherint_8, otherint_9, otherint_11, 
                                          otherint_12))$total[2]
#Smith
smith_extsoo_alpha <- psych::alpha(select(smith_final, otherint_1, otherint_2, otherint_5, 
                                          otherint_6, otherint_10))$total[2]
smith_intsoo_alpha <- psych::alpha(select(smith_final, otherint_3, otherint_4, otherint_7, 
                                          otherint_8, otherint_9, otherint_11, otherint_12))$total[2]

descsplit <- clarksmith_women %>%
  group_by(sexor_A == 1) %>%
  summarize(mean_soo = mean(a2pSOO_A, na.rm = TRUE),
            sd_soo = sd(a2pSOO_A, na.rm = TRUE))

@@

clark_careerasp_alpha <- psych::alpha(select(clark_final, careerasp_1, careerasp_2, 
                                             careerasp_3, careerasp4.r, careerasp_5, 
                                             careerasp_6, careerasp7.r, careerasp_8, 
                                             careerasp_9, careerasp10.r))$total[2]

#Smith
smith_final <- smith_final %>% #reverse code certain career aspiration variables
  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))

@@

#Smith--external and internal
smith_funcTSO_alpha <- psych::alpha(select(smith_final, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
smith_physTSO_alpha <- psych::alpha(select(smith_final, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]

source <- c("@mcfarlin1984remote", 
            "@garcia2016objectification", 
            "@garcia2016objectification", 
            "@garcia2016objectification", 
            "@garcia2016objectification", 
            "@grayobrien2007", 
            "@nollfredrickson1998")

ex_item <- c("he correct answer for the trigram "Quack: Pond: Waddle" would be "Duck"",
             "Questions included aspects of their partner’s internal traits such as personality, friends, family, and extracurricular interests, as well as external traits such as body, appearance, clothing, and body parts. All questions were rated on a scale from 1 (not at all) to 7 (constantly). A positive score in this scale would indicate that the participant thought about their partner’s external traits more than the partner’s internal traits, and a negative score would indicate the opposite",
             " we asked participants to rate the extent to which they felt comfortable, happy, friendly, warm, easygoing, sincere, and authentic on a scale ranging from 1 (not at all) to 7 (very much)
These were combined to form the authenticity scale ($\alpha$ = `r printnum(clark_intauth_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_intauth_alpha)[1,1]` for Sample 2). 	",
"Participants were asked to rank how much they agreed with the following statements: "During the interaction I felt more like a body than a full self" and "I felt more like a body than as a real person in the interaction". Originally, @saguyetal2010 used 3 items, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale ($\alpha$ = `r printnum(clark_howbody_alpha)[1,1]` for Sample 1, and $\alpha$ = `r printnum(smith_howbody_alpha)[1,1]` for Sample 2.)",
""ask someone out on a date," "open the door for your date," "pay for a date," "ask your boyfriend/girlfriend to marry you," "initiate sex with your girlfriend/boyfriend," "initiate condom use during sex," "surprise your boyfriend/ girlfriend with a gift," and "ask your girlfriend/boyfriend to move with you to a new place." Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely).",
"a scale from 0 (not at all true of me) to 4 (very true of me). 
Items include "I hope to become a leader in my career field" and "I hope to move up through any organization or business I work in." Items were fairly reliable ($\alpha$ = `r printnum(clark_careerasp_alpha)[1,1]` for Sample 1, $\alpha$ = `r printnum(smith_careerasp_alpha)[1,1]` for Sample 2).",
"The questionnaire asked participants to rank order both appearance and functional aspects of their bodies, from 1 (least important) to 10 (most important), with respect to physical self-concepts. Of the ten body attributes, five of the items were appearance-based (weight, sex appeal, physical attractiveness, firm/sculpted muscles and body measurements), and five of the items were competence-based (strength, physical coordination, energy level, health and physical fitness). Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1 so that positive scores indicated greater TSO. ")

alpha_s1 <- c()
alpha_s2 <- c()

data.frame(source, ex_item, alpha_s1, alpha_s2)

rownames(corr.table) <- c("Cognitive performance", 
                          "Objectification of partner", 
                          "Authenticity of interaction", 
                          "State self-objectification", 
                          "Relationship agency", 
                          "Career aspirations", 
                          "Trait self objectification (TSO)")

colnames(corr.table)   <- c("Original Source", "Example Item", "Reliability ($\alpha$) Sample 1", "Reliability ($\alpha$) Sample 2")

@@

Relationship agency The scale originally had 9 items, but the 9th item had low correlations with the remaining items, ranging from .02 to .30 for the first sample, and .04 to .30 for the second sample. Therefore, this item was removed. As a result, the 8-item scale had moderately high reliability for both samples ($\alpha$ = `r printnum(clark_relag_alpha)[1,1]` for Sample 1, ($\alpha$ = `r printnum(smith_relag_alpha)[1,1]` for Sample 2).

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---
```{r setup, analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, include = FALSE)
```
```{r packages, warning = FALSE, message = FALSE}
library(papaja)
library(nlme)
library(haven)
library(devtools)
library(psych)
library(mosaic)
#library(dyadr)
library(tidyr)
library(dplyr)
library(irr)
library(apaTables)
library(knitr)
library(kutils)
library(tidyverse)
library(lavaan)
library(xtable)
library(rmarkdown)
```
@robertsfredrickson's Objectification Theory, suggests that, in addition to being steeped in a culture that objectifies women, women are objectified in actual interpersonal encounters. The negative effects of this interpersonal objectification for women have been theorized to be the strongest under the "male gaze," that is, when it is a perceived or actual man doing the objectifying [@calogero2004test; @gervais2011you; @gay2010my], but what are the consequences when a woman objectifies another woman in an interaction? Psychological researchers studying the sexual objectification of women have in recent years explored the interpersonal process of the objectification, finding evidence for *self*-objectification in the target as a proximal consequence of being objectified [@garcia2016objectification; @strelan2018birds; @riemer2020self]. In a recent review, @gervais2020social organized the extant literature on interpersonal self-objectification and proposed a theoretical model called the Social Interaction Model of Objectification (SIMO). The SIMO focuses on understanding mixed-gender interactions, acknowledging the patriarchal power structure embedded in these mixed interactions, but can it be extended to interactions among women? Although there is evidence that women can objectify other women [@loughnan2015exploring; @puvia2013being; @gervais2013my], studies investigating the process of interpersonal objectification in interactions between women is scarce.

@@

```{r}
#Reliabilities and some descriptives

#Cognitive performance - Full sample
mean_trigram <- favstats(~trigram_score_A, data=clarksmith_women)$mean
sd_trigram <- favstats(~trigram_score_A, data=clarksmith_women)$sd

##SOO
#Clark
clark_extsoo_alpha <- psych::alpha(select(clark_final, otherint_1, otherint_2, 
                                          otherint_5, otherint_6, otherint_10))$total[2]
clark_intsoo_alpha <- psych::alpha(select(clark_final, otherint_3, otherint_4, 
                                          otherint_7, otherint_8, otherint_9, otherint_11, 
                                          otherint_12))$total[2]
#Smith
smith_extsoo_alpha <- psych::alpha(select(smith_final, otherint_1, otherint_2, otherint_5, 
                                          otherint_6, otherint_10))$total[2]
smith_intsoo_alpha <- psych::alpha(select(smith_final, otherint_3, otherint_4, otherint_7, 
                                          otherint_8, otherint_9, otherint_11, otherint_12))$total[2]
descsplit <- clarksmith_women %>%
  group_by(sexor_A == 1) %>%
  summarize(mean_soo = mean(a2pSOO_A, na.rm = TRUE),
            sd_soo = sd(a2pSOO_A, na.rm = TRUE))

@@

clark_careerasp_alpha <- psych::alpha(select(clark_final, careerasp_1, careerasp_2, 
                                             careerasp_3, careerasp4.r, careerasp_5, 
                                             careerasp_6, careerasp7.r, careerasp_8, 
                                             careerasp_9, careerasp10.r))$total[2]
#Smith
smith_final <- smith_final %>% #reverse code certain career aspiration variables
  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))

@@

#Smith--external and internal
smith_funcTSO_alpha <- psych::alpha(select(smith_final, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
smith_physTSO_alpha <- psych::alpha(select(smith_final, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2] 
```

```{r measures, include=TRUE, echo=FALSE, results='asis'}
############### TABLE MAKING ###################

source <- c("@mcfarlin1984remote", 
            "@garcia2016objectification", 
            "@garcia2016objectification", 
            "@saguyetal2010", 
            "@garcia2016objectification", 
            "@grayobrien2007", 
            "@nollfredrickson1998")

ex_item <- c("The correct answer for the trigram \"Quack: Pond: Waddle\" would be \"Duck\"",
             "\"During the interaction, how often did you think about your partner’s personality?\" (...friends, family, and extracurricular interests, body, appearance, clothing, and body parts) on a scale from 1 (not at all) to 7 (constantly). A difference between the average internal and exxternal traits is taken",
             "\"During the interaction, to what extent did you feel comfortable?\" (...happy, friendly, warm, easygoing, sincere, and authentic) on a scale ranging from 1 (not at all) to 7 (very much)",
             "\"During the interaction I felt more like a body than a full self\"",
             "\"ask someone out on a date\" Responses were measured on a scale ranging from 1 (not at all likely) to 7 (extremely likely)",
             "\"I hope to become a leader in my career field\"",
             "Participants rank order aspects of their bodies from 1 (least important) to 10 (most important): weight, sex appeal, physical attractiveness, firm/sculpted muscles and body measurements, strength, physical coordination, energy level, health and physical fitness. Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1 so that positive scores indicated greater TSO.")

alpha_s1 <- c("Not avaliable",
paste("external: ", printnum(clark_extsoo_alpha)[1,1], "; internal: ", printnum(clark_intsoo_alpha)[1,1]),
printnum(clark_intauth_alpha)[1,1],
printnum(clark_howbody_alpha)[1,1],
printnum(clark_relag_alpha)[1,1],
printnum(clark_careerasp_alpha)[1,1],
paste("appearance: ", printnum(clark_physTSO_alpha)[1,1], "; competence: ", printnum(clark_funcTSO_alpha)[1,1]))

alpha_s2 <- c("Not avaliable",
paste("external: ", printnum(smith_extsoo_alpha)[1,1], "; internal: ", printnum(smith_intsoo_alpha)[1,1]),
printnum(smith_intauth_alpha)[1,1],
printnum(smith_howbody_alpha)[1,1],
printnum(smith_relag_alpha)[1,1],
printnum(smith_careerasp_alpha)[1,1],
paste("appearance: ", printnum(smith_physTSO_alpha)[1,1], "; competence: ", printnum(smith_funcTSO_alpha)[1,1]))

meas_table <- data.frame(source, ex_item, alpha_s1, alpha_s2)

rownames(meas_table) <- c("Cognitive performance", 
                          "Objectification of partner", 
                          "Authenticity of interaction", 
                          "State self-objectification", 
                          "Relationship agency", 
                          "Career aspirations", 
                          "Trait self objectification (TSO)")

colnames(meas_table)   <- c("Original Source", "Example Item", "Reliability ($\alpha$) Sample 1", "Reliability ($\alpha$) Sample 2")

apa_table(meas_table, caption="Measures", escape=FALSE)
```

@@

Howbody used 3 items, but in both samples the reliability of the scale was higher once the third item was removed, so we chose to only use the first two for our measure of SSO, leaving us with a reliable scale (see Table\ \@ref(tab:measures)).

Relationship agency The scale originally had 9 items, but the 9th item had low correlations with the remaining items, ranging from .02 to .30 for the first sample, and .04 to .30 for the second sample. Therefore, this item was removed. As a result, the 8-item scale had moderately high reliability for both samples (see Table\ \@ref(tab:measures)).
